Exploratory Analysis Ethan Schilling

### 2025-12-10 Exploratory Analysis Ethan SchillingREAL.Rmd

```{r}
library(tidyverse)
library(knitr)
library(tidymodels)
library(dplyr)
library(Metrics)
```

@@

saveRDS(TDS_plot,"TDS_plot.rds")
saveRDS(TOC_plot,"TOC_plot.rds")
saveRDS(DOC_plot,"DOC_plot.rds")

@@

getwd()
```

@@

@@

>>>>

```{r}
library(tidyverse)
library(knitr)
library(tidymodels)
library(dplyr)
library(Metrics)
library(kableExtra)
```

@@

#saveRDS(TDS_plot,"TDS_plot.rds")
#saveRDS(TOC_plot,"TOC_plot.rds")
#saveRDS(DOC_plot,"DOC_plot.rds")

@@

@@

# All predictors

model0 <- lm(FeCl_dose ~ mean_Temp + mean_pH + mean_Conductivity + mean_Turbidity + Temp_lag1 + Temp_lag2 + pH_lag1 + pH_lag2 + Cond_lag1 + Cond_lag2 + Turb_lag1 + Turb_lag2, data = train)

test$pred_model0 <- predict(model0, newdata = test)

cat("Model 0 RMSE:", rmse(test$FeCl_dose, test$pred_model0), "\n")
cat("Model 0 MAE :", mae(test$FeCl_dose, test$pred_model0), "\n")

@@

model_descriptions <- c(
  "Main effects only",
  "Temp × pH interaction",
  "Temp × pH + Cond × Turb interactions",
  "Temp × Cond interaction",
  "Cond × pH + Temp × Cond interactions"
)

results <- data.frame(
  Model = paste0("Model ", 0:4),
  RMSE = c(
    rmse(test$FeCl_dose, test$pred_model0),
    rmse(test$FeCl_dose, test$pred_model1),
    rmse(test$FeCl_dose, test$pred_model2),
    rmse(test$FeCl_dose, test$pred_model3),
    rmse(test$FeCl_dose, test$pred_model4)
  ),
  MAE = c(
    mae(test$FeCl_dose, test$pred_model0),
    mae(test$FeCl_dose, test$pred_model1),
    mae(test$FeCl_dose, test$pred_model2),
    mae(test$FeCl_dose, test$pred_model3),
    mae(test$FeCl_dose, test$pred_model4)
  ),
  Description = model_descriptions
)

results <- results %>%
  mutate(
    RMSE = round(RMSE, 3),
    MAE  = round(MAE, 3)
  ) %>%
  arrange(RMSE)

best_rmse <- min(results$RMSE)
best_mae  <- min(results$MAE)

results %>%
  kable("html", caption = "Model Performance Summary ") %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "center"
  ) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(4, width = "20em") %>%
  row_spec(which(results$RMSE == best_rmse), background = "#d4edda") %>%  
  row_spec(which(results$MAE == best_mae), background = "#cfe2f3")
